Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-10 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Added...

>>>>

\section{Expectation Values for IVPMs\label{sec:ExpectationValue}}

We may need to understand how to define expectation values of an observable
for quantum IVPMs. Recall an observable is the quantum version of
a random variable. Hence, in order to define expectation values of
an observable, we need to understand the definition of expectation
values of a random variable for an classical IVPM.
